### 2025-05-15 manuscript/manuscript.Rmd
Remove a tilde
I must have put it in there from my LaTeX habit...

We sincerely thank Paul Conn for his thoughtful and thorough review, 
which greatly improved this manuscript. We would like to thank Rob Ahrens whose
ADMB model code provided as part of his excellent fishery stock assessment class
served as the basis for the assessment model developed in this paper.
A portion of the writing and code development for this paper occurred while
CF and ECA were scientists-in-residence with Matthew G.~DeSaix at the
mobile High Altitude Venue for Ecological Analysis, Genetics and
Statistics on location in Moab, Utah
during April 2023.  This is contribution mHAVEAGAS-004.

>>>>

We sincerely thank Paul Conn for his thoughtful and thorough review, 
which greatly improved this manuscript. We would like to thank Rob Ahrens whose
ADMB model code provided as part of his excellent fishery stock assessment class
served as the basis for the assessment model developed in this paper.
A portion of the writing and code development for this paper occurred while
CF and ECA were scientists-in-residence with Matthew G. DeSaix at the
mobile High Altitude Venue for Ecological Analysis, Genetics and
Statistics on location in Moab, Utah
during April 2023.  This is contribution mHAVEAGAS-004.
